TBD

### 2021-03-06 outputs/paper/paper.Rmd
update

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(kableExtra)
```

@@

### treat distribution 
```{r treat, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
EDA<-EDA%>%
  drop_na(treat)

@@

### internet usage by meta.os
```{r internet, fig.cap = "internet usage by os",echo=FALSE, fig.width=5, fig.height=4}

@@

ggplot(EDA, aes(x = post_favor_Sanders,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  theme_minimal()

#bar chart

post_S<-EDA%>%
  group_by(treat)%>%
  summarise(Average_mark=mean(post_favor_Sanders))

ggplot(aes(x=treat,y=Average_mark),data=post_S)+
  geom_bar(stat="identity",fill=c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  xlab("Feelings towards Sanders")

```
### Average deception level by treat
```{r table1,tab.cap="Average deception level of each media format", echo = FALSE,warning=FALSE}
EDA%>%
  group_by(treat)%>%
  filter(treat != "control")%>%
  summarise("Average Deception Level"=mean(believed_true,na.rm = T))%>%
  knitr::kable(caption = "Average deception level of each media format")
```

>>>>

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(hrbrthemes)
library(kableExtra)

@@

### treat distribution 
```{r treat, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}

EDA<-EDA%>%
  drop_na(treat)

@@

## internet usage frequency by education level
```{r internet, fig.cap = "internet usages",echo=FALSE, fig.width=15, fig.height=5}

G1<-ggplot(EDA, aes(x=internet_usage, fill=EDA$educ)) + 
    geom_area(alpha=0.8 , size=0.2, colour="black", stat = "count")+
    labs(title = "Internet usage frequency by education level ",y="Counts",x="Days")+
    scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6"))

G2<-ggplot(EDA, aes(x=internet_usage, fill=EDA$meta_OS)) + 
    geom_area(alpha=0.8 , size=0.2, colour="black", stat = "count")+
    labs(title = "Internet usage frequency by devices ",y="Counts",x="Days")+
    scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6"))

G3<-ggplot(EDA, aes(x=internet_usage, fill=EDA$age_65)) + 
    geom_area(alpha=0.8 , size=0.2, colour="black", stat = "count")+
    labs(title = "Internet usage frequency by age group ",y="Counts",x="Days")+
    scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6"))

# combine two diagram in one graph
ggarrange(
  G1, G2, G3, 
  ncol = 3, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )
```

ggplot(EDA, aes(x = post_favor_Sanders,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  theme_minimal()

@@

### Average deception level by treat
```{r table1,tab.cap="Average deception level of each media format", echo = FALSE,warning=FALSE}
EDA%>%
  group_by(treat)%>%
  filter(treat != "control")%>%
  summarise("Average Deception Level"=mean(believed_true,na.rm = T))%>%
  knitr::kable(caption = "Average deception level of each media format")
```
